---
title: "RUE Fodder Beet"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)

```

## Read and clean data

* Note that only points before canopy senescence were used for RUE calculation

```{r Read, include=TRUE, echo=FALSE}

fileFolder <- "C:\\GitHubRepos\\FodderBeetRUE_2016\\"

info <- read.table(paste0(fileFolder, "RUE.txt"), header = TRUE)

str(info)

info$N_Treatments <- as.factor(info$N_Treatments)
info$UseForRUE <- as.factor(info$UseForRUE)
info$Date <- dmy(info$Date )
info$Total_DM <- info$Total_DM*100 # kg/ha to g/m2

summary(info)

```

# Check individual points

* Data at final point of analysis
* Do not consider full set

```{r, echo=FALSE, fig.height=4, fig.width=8}
head(info)

info %>%
  filter(Stage=="end_analysis")  %>%
  select(Experiment, N_Treatments, Water_Treatments, Water_treat_level, Date, Total_DM, Interception) %>%
#  tidyr::gather("Variable","Value",Total_DM:Interception) %>%
  ggplot(aes(x=N_Treatments, y=Total_DM)) +
  geom_point() +
  facet_grid(Experiment~Water_treat_level, scales= "free")

head(info)



```
Light Interception

* Also at end point of analysis
* Due to teh lack of effect of irrigation frequency on biomass or interception, data from all irrigation frequencies will be analysed as "irrigated" (FIXME: triple-check if this is the case)

```{r}
info %>%
  filter(Stage=="end_analysis")  %>%
  select(Experiment, N_Treatments, Water_Treatments, Water_treat_level, Date, Total_DM, Interception) %>%
#  tidyr::gather("Variable","Value",Total_DM:Interception) %>%
  ggplot(aes(x=N_Treatments, y=Interception)) +
  geom_point() +
  facet_grid(Experiment~Water_treat_level)
```

## Check how irrig x rain-fed data looks

```{r}

info %>%
  filter(Stage=="end_analysis")  %>%
  select(Experiment, N_Treatments, Water_Treatments, Water_treat_level, Date, Total_DM, Interception) %>%
tidyr::gather("Variable","Value",Total_DM:Interception) %>%
  ggplot(aes(x=N_Treatments, y=Value, colour=Water_Treatments)) +
  geom_point() +
  facet_wrap(Variable~Experiment, scales="free")


```

## Plot time series

```{r TimeSeries, echo=FALSE, warning=FALSE,fig.height=4, fig.width=8}

info %>%
 # dplyr::select(-Shoot_DM, -Bulb_DM) %>%
  mutate(Total_DM=Total_DM*10/1000) %>%
  tidyr::gather("Variable", "Value",11:12) %>%
  mutate(Variable = as.factor(Variable))  %>%
  group_by(Experiment, N_Treatments, Water_Treatments,         Date, Variable) %>%
  # Water_treat_level, Potential, Date, Variable) %>%
  summarise_each(funs(mean, sd)) %>%
  mutate(Variable = factor(Variable, levels=c("Total_DM", "Interception"))) %>%
  ggplot(aes(x=Date,y=Value_mean, 
             colour=factor(Water_Treatments),
             linetype=factor(N_Treatments),
             shape=factor(N_Treatments))) +
  geom_point(size=2) +
  geom_line(aes(linetype=factor(Water_Treatments))) +
  facet_grid(Variable~Experiment, scales= "free") +
  ylab("IPAR (MJ/m2)         W (t DM/ha)") +
  xlab("Measurement date") +
  geom_errorbar(aes(ymin=Value_mean-Value_sd,
                    ymax=Value_mean+Value_sd), 
                width=0.25) +
  theme(strip.text.y = element_blank()) +
  scale_linetype_discrete(guide = FALSE) +
  theme(legend.position="top") +
  labs(shape="N supply (kg/ha)", 
        colour = "Water supply") # +
#  theme(legend.title=element_blank(),strip.text.y = element_blank())
#  theme(legend.title=element_blank())
  
  
```

## Biomass (used for RUE) vs. N

```{r N_effect, echo=FALSE, warning=FALSE,fig.height=4, fig.width=8}


# select last point used in RUE regression analysis

# biomass
info %>%
  filter(Stage == "end_analysis") %>%
  group_by(Experiment, N_Treatments, Water_Treatments, Potential) %>%
  summarise_each(funs(mean, sd)) %>%
  mutate(Potential = factor(Potential, levels=c("Potential", "Limited"))) %>%
  ggplot(aes(x=N_Treatments,y=Total_DM_mean, 
             shape=factor(Experiment),
             colour=factor(Water_Treatments))) +
  geom_point(size=2) +
  geom_smooth(aes(fill=factor(Water_Treatments)),se = TRUE, method="lm") +
  ylab("Total biomass (g/m2) ") +
  xlab(" N rate (kg N/ha)") +
  geom_errorbar(aes(ymin=Total_DM_mean-Total_DM_sd,
                    ymax=Total_DM_mean+Total_DM_sd), 
                width=0.3)  +
  labs(shape="Experiment", 
        colour = "Water supply") 



```

# Light interception for last point used for rue analyses vs N rates

```{r, warning=FALSE,fig.height=4, fig.width=8}

# select last point used in RUE regression analysis
# light interception
info_av <- info %>%
  filter(Stage == "end_analysis") %>%
  group_by(Experiment, N_Treatments, Water_Treatments, Water_treat_level, Potential) %>%
  filter(Interception == max(Interception)) %>%
  summarise_each(funs(mean, sd)) 


info_av %>%
  ggplot(aes(x=N_Treatments,y=Interception_mean, 
             colour=factor(Water_Treatments))) +
  geom_point(size=2.5,aes(shape=factor(Water_treat_level))) +
  geom_smooth(aes(linetype=factor(N_Treatments)),se = TRUE, method="lm") +
  ylab("Intercepted light (MJ/m2) ") +
  xlab(" N rate (kg N/ha)") +
  geom_errorbar(aes(ymin=Interception_mean-Interception_sd,
                    ymax=Interception_mean+Interception_sd,width=0.15) 
                ) +
 # facet_wrap(Experiment~Potential, ncol=3)
   facet_grid(.~Experiment)+
  theme(legend.title=element_blank())+
  ylim(0,max(info_av$Interception_mean))
```

# Runs ANOVA for interception

```{r}

df_int <- info %>% 
  filter(UseForRUE == "Yes") %>%
  select(Experiment, N_Treatments, Water_Treatments, Water_treat_level,Rep, Interception) 

df_int$Rep <- as.factor(df_int$Rep)

str(df_int)

exp <- unique(info$Experiment)


for(e in 1:length(exp)) {
  
  if(e == 1) {
    
anova <- NULL
df <- NULL
df <- df_int %>% subset(Experiment == exp[e])

anova <- aov(Interception ~ N_Treatments+Rep, data = df)
print("############## EXP A ##############")
print(" ")
print(summary(anova))
print(TukeyHSD(anova))

    
  } else if (e == 2) {
    
anova <- NULL
df <- NULL
df <- df_int %>% subset(Experiment == exp[e])
 
  
anova <- aov(Interception ~ N_Treatments*Water_Treatments+Rep, data = df)
print("############## EXP B ##############")
print(" ")
print(summary(anova))
print(TukeyHSD(anova))
    
  }  else if (e == 3) {
    
anova <- NULL
df <- NULL
df <- df_int %>% subset(Experiment == exp[e])

anova <- aov(Interception ~ Water_Treatments+Rep, data = df)
print("############## EXP C ##############")
print(" ")
print(summary(anova))
print(TukeyHSD(anova))
    
  }
  
}
```

- RUE is estimated between first and last harvest when biomass still increases quasi-linearly (picked by eye)
- Not forcing to zero due to potential bias
- First biomass harvest is at very high interception (biased overestimation of RUE?)

```{r pressure, echo=FALSE, echo=FALSE, warning=FALSE,fig.height=4, fig.width=8}
df_rue_all <-  info %>%
#  filter(UseForRUE == "Yes") %>% # Only use points in which biomass increases (i.e. no senescence)
  group_by(Experiment,UseForRUE, N_Treatments, Water_Treatments,Date, Potential) %>%
  mutate(Total_DM = Total_DM) %>% # from t/ha to g/m2
  summarise_each(funs(mean,sd)) %>%
  mutate(Potential = factor(Potential, levels=c("Potential", "Limited"))) 

df_rue_yes <-  df_rue_all %>%
  filter(UseForRUE == "Yes")

df_rue_yes %>%
  ggplot(aes(x=Interception_mean,y=Total_DM_mean, 
             shape=factor(N_Treatments),
             colour=factor(Water_Treatments))) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, aes(linetype=factor(N_Treatments))) +
  geom_point(data=df_rue_all,aes(x=Interception_mean,y=Total_DM_mean,
                                 colour=factor(Water_Treatments),
              
                                 shape=factor(N_Treatments)
                                 ))+
  ylab("Total biomass (g/m2) ") +
  xlab(" Light interception (MJ/m2)") +
  geom_errorbar(aes(ymin=Total_DM_mean-Total_DM_sd,
                    ymax=Total_DM_mean+Total_DM_sd)) +
 # facet_wrap(~N_Treatments, ncol=3)
 facet_grid(.~Experiment) +
theme(legend.title=element_blank())


```
## calculate RUE
```{r RUECalc, echo=FALSE, warning=FALSE, include=TRUE,fig.height=4, fig.width=8}

# calculate RUE per plot

# head(info)

# create index for each rep (observation period and unit as a rueChunk)
info_filtered <- info %>% # FIXME: Now there's a filter of which points to use - change name
filter(UseForRUE == "Yes") %>%
mutate(rueChunk = paste0(Experiment,"_", 
                         N_Treatments,"_" ,
                         Water_treat_level,"_", 
                         Rep))

rounds <- unique(info_filtered$rueChunk)

# loop through all the individual periods/treats/experiments
resTable <- data.frame(NULL)

for(i in 1:length(rounds)) {
  
 thisStat <- NULL
  
 buf <- info_filtered[info_filtered$rueChunk == rounds[i],]
 
 bio <- buf$Total_DM 
 interc  <- buf$Interception
  
  n_s <- length(bio)
  n_m <- length(interc)
  model <- lm(bio~interc)
  bio_sq <- sum((bio - mean(bio))^2)
  int_sq <- sum((interc - mean(interc))^2)
  r2 <- summary(model)$r.squared
  slope <- model$coefficients[[2]]
  slope_sig <- summary(model)$coefficients[8]
  int <- model$coefficients[[1]]
  int_sig <- summary(model)$coefficients[7]
  bio_max <- max(bio)
  light_max <- max(interc)  
  
 thisStat <- data.frame(Exp = buf$Experiment[1], 
                        N_treat = buf$N_Treatments[1], 
                        W_treat = buf$Water_Treatments[1],
                        W_treat_lev = buf$Water_treat_level[1],
                        Rep = buf$Rep[1],
                        n = n_s,
                        RUE = slope, 
                        slope_dif_zero = round(slope_sig,digits=3),
                        intercept=int,
                        int_dif_zero = int_sig,
                        bio_max = bio_max,
                        light_max = light_max,
                        R2=r2)
 
 if(i==1) {
   resTable <- thisStat
 } else {
   resTable <- rbind(resTable,thisStat)
 }
}

resTable$Rep <- as.factor(resTable$Rep)
head(resTable)


```

```{r, echo=FALSE,fig.height=8, fig.width=8}
summary(resTable)

print("Range in RUE estimates (fractional): ")
max(resTable$RUE)/min(resTable$RUE)
```

## Check all RUE estimates

```{r,fig.height=4, fig.width=8}
resTable %>%
  ggplot(aes(x=N_treat, y=RUE, colour=W_treat_lev)) +
  geom_point() +
  facet_grid(.~Exp) +
  ylim(0,max(resTable$RUE))
```

```{r}
resTable %>%
  kable(format = "markdown", digits = 2)

```


```{r SaveRUE}
write.csv(resTable, "RUE_stats.csv")
```


```{r, warning=FALSE,fig.height=4, fig.width=8}

x <- resTable %>%
  group_by(Exp, N_treat, W_treat, W_treat_lev) %>%
  summarise_each(funs(mean, sd))


# graph
resTable %>%
  group_by(Exp, N_treat, W_treat,W_treat_lev) %>%
 # filter(Exp != "W-") %>%
  dplyr::select(RUE) %>%
  summarise_each(funs(mean, sd)) %>%
  ggplot(aes(x=as.numeric(as.character(N_treat)), y=as.numeric(mean),
             colour=factor(W_treat))) +
  geom_point(size = 2, aes(shape=factor(Exp))) +
 # geom_line() +
  geom_smooth(method="lm", aes(fill=W_treat), alpha=0.2) +
#  facet_grid(.~Exp) +
  ylab("Radiation use efficiency (g/MJ) ") +
  xlab("N fertiliser rate (kg N/ha)")+
  geom_errorbar(aes(ymin=mean-sd,
                    ymax=mean+sd), width = 0.25) +
 # theme(legend.title=element_blank()) +
  labs(shape="Experiment", 
        colour = "Water supply") +
  scale_fill_discrete(guide = FALSE) 


```

# give stats linear coeff

```{r}
resTable %>% 
  ungroup() %>%
  mutate(RUE = as.numeric(RUE)) %>%
  mutate(N_treat = as.numeric(as.character(N_treat))) %>%
  group_by(Exp,W_treat) %>%
  do(mod = lm(RUE ~ N_treat, data = .)) %>%
  mutate(Intercept = summary(mod)$coeff[1]) %>% # slope
  mutate(Slope = summary(mod)$coeff[2]) %>%
  mutate(R2 = summary(mod)$r.squared) %>%
  mutate(Pvalue=summary(mod)$coeff[8]) %>%
  select(-mod)
```



```{r NormRUE, warning=FALSE}
# normalise within each experiment
rue_norm <- resTable %>%
  group_by(Exp, N_treat, W_treat, W_treat_lev) %>% # to average by treatment level
  dplyr::select(RUE) %>% # FIXME: why three similar values???
  mutate(RUE_av=mean(RUE)) %>%
  dplyr::select(RUE_av) %>%
  ungroup() %>%
  group_by(Exp) %>% # to select the maximum of treatment average
  mutate(RUEmax = max(RUE_av)) %>%
  mutate(RUEnorm = RUE_av/RUEmax) %>%
  group_by(Exp, N_treat, W_treat, W_treat_lev) %>% # quick fix to remove duplicated lines
  summarise_each(funs(mean))
  

head(rue_norm)

write.csv(rue_norm,"RUE_Normalised.csv" )


```

```{r}
summary(rue_norm)
```


```{r, warning=FALSE}

# FIXME: Ask Esther if this averaging by Experiment is acceptable

# rue_norm_av <- rue_norm  %>% 
#   filter(Exp!="W-") %>%
#   group_by(N_treat,W_treat) %>%
#   summarise_each(funs(mean, sd)) 

graphRUEnorm <- rue_norm %>%
 # filter(Exp!="W-") %>%
  ggplot(aes(x=as.numeric(as.character(N_treat)), y=as.numeric(RUEnorm),
             colour=factor(W_treat))) +
  geom_point(aes(shape=factor(Exp)),size = 4) +
 # geom_line() +
  geom_smooth(aes(fill=factor(W_treat)),se = TRUE, method="lm", alpha=0.2) +
  ylab("Normalised radiation use efficiency (0-1) ") +
  xlab(" N rate (kg N/ha)") +
     # geom_errorbar(aes(ymin=RUEnorm_mean-RUEnorm_sd, # not averaged anymore
     #                 ymax=RUEnorm_mean+RUEnorm_sd), width = 0.5) +
  ylim(0.0, 1.05) +
 # facet_grid(.~Exp)+
  theme(legend.title=element_blank()) + 
  theme(legend.position="top") 

graphRUEnorm
```

# Give linear coefficients 

```{r}

rue_norm %>% 
  ungroup() %>%
  mutate(RUEnorm_mean = as.numeric(RUEnorm)) %>%
  mutate(N_treat = as.numeric(as.character(N_treat))) %>%
  group_by(Exp,W_treat) %>%
  do(mod = lm(RUEnorm_mean ~ N_treat, data = .)) %>%
  mutate(Intercept = summary(mod)$coeff[1]) %>% # slope
  mutate(Slope = summary(mod)$coeff[2]) %>%
  mutate(R2 = summary(mod)$r.squared) %>%
  mutate(Pvalue=summary(mod)$coeff[8]) %>%
  select(-mod)

```

## ANOVA RUE

- not tested yet

```{r ANOVA, echo=FALSE}

str(resTable)

exp <- unique(resTable$Exp)


for(e in 1:length(exp)) {
  
  if(e == 1) {
    
anova <- NULL
df <- NULL
df <- resTable %>% subset(Exp == exp[e])

anova <- aov(RUE ~ N_treat+Rep, data = df)
print("############## EXP A ##############")
print(" ")
print(summary(anova))
print(TukeyHSD(anova))

    
  } else if ( e == 2) {
    
anova <- NULL
df <- NULL
df <- resTable %>% subset(Exp == exp[e])
 
  
anova <- aov(RUE ~ N_treat*W_treat_lev+Rep, data = df)
print("############## EXP B ##############")
print(" ")
print(summary(anova))
print(TukeyHSD(anova))
    
  }  else if (e == 3) {
    
anova <- NULL
df <- NULL
df <- resTable %>% subset(Exp == exp[e])

anova <- aov(RUE ~ W_treat_lev+Rep, data = df)
print("############## EXP C ##############")
print(" ")
print(summary(anova))
print(TukeyHSD(anova))
    
  }
  
}

```



## ANOVA light

- not tested yet

```{r ANOVA2, echo=FALSE}

str(resTable)

exp <- unique(resTable$Exp)

for(e in 1:length(exp)) {
  
  if(e == 1) {
    
anova <- NULL
df <- NULL
df <- resTable %>% subset(Exp == exp[e])

anova <- aov(light_max ~ N_treat+Rep, data = df)
print("############## EXP A ##############")
print(" ")
print(summary(anova))
print(TukeyHSD(anova))

    
  } else if ( e == 2) {
    
anova <- NULL
df <- NULL
df <- resTable %>% subset(Exp == exp[e])
 
  
anova <- aov(light_max ~ N_treat*W_treat_lev+Rep, data = df)
print("############## EXP B ##############")
print(" ")
print(summary(anova))
print(TukeyHSD(anova))
    
  }  else if (e == 3) {
    
anova <- NULL
df <- NULL
df <- resTable %>% subset(Exp == exp[e])

anova <- aov(light_max ~ W_treat_lev+Rep, data = df)
print("############## EXP C ##############")
print(" ")
print(summary(anova))
print(TukeyHSD(anova))
    
  }
  
}

```




```{r,fig.height=4, fig.width=8}

info %>%
  mutate(Total_DM = Total_DM/100) %>% # back dfrom g/m2 to kg/ha
  mutate(HI=Bulb_DM/Total_DM*100) %>%
  group_by(Date, Experiment, N_Treatments, Water_Treatments, Water_treat_level) %>%
  summarise(Total_DM= mean(Total_DM), HI_sd = sd(HI), HI = mean(HI)) %>%
#  summary() %>%
  ggplot(aes(x=Total_DM, y=HI, linetype=Water_Treatments)) +
  geom_point(aes(shape=factor(N_Treatments), colour=factor(Water_Treatments))) +
  geom_smooth() +
#  facet_grid(.~Experiment, scale= "free") +
   scale_linetype_discrete(guide = FALSE) +
  theme(legend.position="top") +

  ylab("Storage root in total biomass (%)") +
  xlab("Total crop biomass (kg/ha)") +
  ylim(0,100)+
  labs(linetype="Water supply", colour="Water supply level", shape="Nitrogen supply") +     
  geom_errorbar(aes(ymin=HI-HI_sd,
                    ymax=HI+HI_sd), 
                width=0.25, colour="darkgrey")
  

```


