---
title: "Untitled"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(segmented)

```

```{r Read}
fileFolder <- "C:\\GitHubRepos\\FodderBeetRUE_2016\\"

info <- read.table(paste0(fileFolder, "RUE.txt"), header = TRUE)

str(info)

info$N_Treatments <- as.factor(info$N_Treatments)
info$Date <- dmy(info$Date )
info$Total_DM <- info$Total_DM*100 # kg/ha to g/m2

summary(info)
```


## Test SLN vs Pn

- raw data all points

```{r}

info %>%
  ggplot(aes(x=SLN, y=Pn, colour=N_Treatments))+
  geom_point(aes(shape=Water_treat_level)) + 
  facet_grid(.~Water_Treatments)

```

## Normalise Pn values

- Use only final harvest samples (rationale: )
- Use only irrigated plots (rationale: )
- Find maximum by Experiment
- Average values by N treatment
- Calculate normalised Pn by N treatment in relation to maximum Pn by treatment (rationale: instantaneous wheather conditions vary too much and affect Pn ... therefore better reduce noise using relative values)

```{r NormalisePn}

df_Pn_norm <- info %>%
  dplyr::filter(Stage == "final") %>%
  dplyr::filter(Water_Treatments == "Irrigated") %>%
  na.omit() %>%
#  group_by(Experiment, N_Treatments,Water_Treatments) %>%
  group_by(Experiment, N_Treatments) %>%
  summarise(Pn_sd = sd(Pn), SLN_sd = sd(SLN), Pn = mean(Pn), SLN = mean(SLN)) %>%
  mutate(Pn_mx = max(Pn)) %>%
  mutate(Pn_norm = Pn/Pn_mx) %>%
  mutate(Pn_sd_norm = Pn_sd/Pn_mx)

summary(df_Pn_norm)

```

```{r}
df_Pn_norm %>%
  kable(format = "markdown", digits = 2)
```


```{r BrokenStickStats}

      out.lm<-lm(SLN~Pn_norm,data=df_Pn_norm)

# FIXME: Not able to find break

      # o <- segmented(out.lm,seg.Z=~SLN,psi=list(SLN=c(2.42)),
      #              control=seg.control(display=FALSE))
      # # show stats
      # print(summary(o))
      # 
      # # find slope
      # s = slope(o)
      # s$SLN[2,1]
      # 
      # # find estimated break
      # b = o$psi[,2]

# forced by hand now at the moment: 
b <- 2.47
      
      print(paste0("Break-point is:", b))
      
```

```{r Pn_norm_graph}

df_Pn_norm %>%
  ggplot(aes(x=SLN, y=Pn_norm, colour=N_Treatments)) +
  geom_segment(aes(x = min(SLN), xend = b, y = 0.84, yend = 1), 
               linetype=1, colour ="black", size=1.2) +
  geom_segment(aes(x = b, xend = max(SLN), y = 1, yend = 1), linetype=1, colour ="black", size=1.2) +
  geom_point(aes(shape=Experiment)) +
  geom_errorbar(aes(ymin=Pn_norm-Pn_sd_norm/2,
                    ymax=Pn_norm+Pn_sd_norm/2)) +
 # facet_grid(.~Experiment) +
  geom_errorbarh(aes(xmin = SLN-SLN_sd/2,
                     xmax = SLN+SLN_sd/2)) +
  xlab("Specific Leaf Nitrogen (SLN, g N/cm2)") +
  ylab("Normalised maximum\n photosynthetic rate (fractional)")

```

