---
title: "Untitled"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(segmented)

```

```{r Read}
fileFolder <- "C:\\GitHubRepos\\FodderBeetRUE_2016\\"

info <- read.table(paste0(fileFolder, "RUE.txt"), header = TRUE)

str(info)

info$N_Treatments <- as.factor(info$N_Treatments)
# as.Date(info$Date, "%m/%d/%Y")
info$Date <- dmy(info$Date) # FIXME: Had some problems not parsing this format - not sure why
info$Total_DM <- info$Total_DM*100 # kg/ha to g/m2

summary(info)

str(info$Date)
```


## Test SLN vs Pn

- raw data all points

```{r, fig.height=8, fig.width=8}

info %>%
  ggplot(aes(x=SLN, y=Pn, colour=N_Treatments))+
  geom_point(aes(shape=Water_treat_level)) + 
  facet_grid(.~Water_Treatments)

```

## Normalise Pn values

- Find maximum by Experiment and Date
- Average values by N treatment
- Calculate normalised Pn by N treatment in relation to maximum Pn by treatment (rationale: instantaneous wheather conditions vary too much and affect Pn ... therefore better reduce noise using relative values)

```{r NormalisePn}

# maximum Pn of a given day and treatmnet
df_Pn_max <- info %>%
  na.omit() %>%
  group_by(Experiment, Date) %>%
  summarise(Pn_max = max(Pn)) 

head(df_Pn_max)

```

```{r}
# merge it with original
df_Pn_norm <- merge(info, df_Pn_max, by = c("Experiment", "Date"))

df_Pn_norm <- df_Pn_norm %>%
mutate(Pn_norm = Pn/Pn_max*100)
```

```{r}
summary(df_Pn_norm)
```


```{r}
head(df_Pn_norm)
```

## Plot normalised values

```{r, fig.height=8, fig.width=8}

# plot
df_mean <- df_Pn_norm %>%
  group_by(Date, Experiment, N_Treatments, Water_Treatments, Water_treat_level, Potential) %>%
  dplyr::select(SLN, Pn_norm, Pn) %>%
  na.omit() %>%
  summarise_each(funs(mean, sd))


```


```{r FindClusters}

clusNo <- 4 # selected from sensitivity cluster analysis below

myClus <- kmeans(df_mean[,c("SLN_mean","Pn_mean")], centers = clusNo)

myClus_res.within.ss <- sum(myClus$withinss)

clusterClass <- myClus$cluster

dftemp1 <- cbind(df_mean, clusterNo = factor(clusterClass))

# add numbers
dftemp2 <- data.frame(myClus$centers)
dftemp2 <- dftemp2[order(dftemp2$Pn_mean, decreasing = TRUE), ] # FIXME: not working for label order
dftemp2$clusterLabel <- as.factor(paste0("Pn: ",round(dftemp2$Pn_mean,1)," mmols/m2/s and SLN: ",round(dftemp2$SLN_mean,1)," g N/m2"))

dftemp2$clusterNo <- c(1:clusNo)
dftemp2$clusterNo <- as.numeric(dftemp2$clusterNo)
dftemp2$Pn_mean <- NULL
dftemp2$SLN_mean <- NULL

df_cluster <- merge(dftemp1,dftemp2, by="clusterNo")
df_cluster <- df_cluster[order(df_cluster$Pn_mean,df_cluster$clusterLabel, decreasing = TRUE), ] # FIXME: not working

```

## Plot absolute values

- 4th cluster has only 3 points so no elipse can be calculated

```{r, fig.height=8, fig.width=8}
# plot
g_abs <- df_cluster %>%
  ggplot(aes(x=SLN_mean , y=Pn_mean, linetype = clusterLabel)) +
  geom_point(aes(colour=N_Treatments, shape=Water_treat_level), size =3) +
    geom_errorbar(aes(ymin=Pn_mean-Pn_sd/2,
                    ymax=Pn_mean+Pn_sd/2), width = 0.0, colour = "darkgrey") +
    geom_errorbarh(aes(xmin=SLN_mean-SLN_sd/2,
                    xmax=SLN_mean+SLN_sd/2), colour = "darkgrey")+
  ylab("Photosynthetic rate (mmol/m2/s)") +
  xlab("") +
 # facet_grid(Experiment~.) +
  stat_ellipse(type = "t") +
  theme(legend.title=element_blank()) #+ theme(legend.position="none")

g_abs

# FIXME: Need to order Pn decreasing

```




```{r FindClusters}

clusNo <- 4 # selected from sensitivity cluster analysis below

myClus <- kmeans(df_mean[,c("SLN_mean","Pn_norm_mean")], centers = clusNo)

myClus_res.within.ss <- sum(myClus$withinss)

clusterClass <- myClus$cluster

dftemp1 <- cbind(df_mean, clusterNo = factor(clusterClass))

# add numbers
dftemp2 <- data.frame(myClus$centers)
dftemp2 <- dftemp2[order(dftemp2$Pn_norm_mean, decreasing = TRUE), ] # FIXME: not working for label order
dftemp2$clusterLabel <- as.factor(paste0("Pn: ",round(dftemp2$Pn_norm_mean,1),"% maximum and SLN: ",round(dftemp2$SLN_mean,1)," g N/m2"))

dftemp2$clusterNo <- c(1:clusNo)
dftemp2$clusterNo <- as.numeric(dftemp2$clusterNo)
dftemp2$Pn_norm_mean <- NULL
dftemp2$SLN_mean <- NULL

df_cluster <- merge(dftemp1,dftemp2, by="clusterNo")
df_cluster <- df_cluster[order(df_cluster$Pn_norm_mean,df_cluster$clusterLabel, decreasing = TRUE), ] # FIXME: not working

```



## Graph normalised Pn

- Pn divideed by the maximum Pn pf a give "date" and "experimnent"
- Aim is to reduce some of the noise from instantaneous Pn readings in response to time/location

```{r}
g_norm <- df_cluster %>%
  ggplot(aes(x=SLN_mean , y=Pn_norm_mean, linetype = clusterLabel)) +
  geom_point(aes(colour=N_Treatments, shape=Water_treat_level), size = 3) +
    geom_errorbar(aes(ymin=Pn_norm_mean-Pn_norm_sd/2,
                    ymax=Pn_norm_mean+Pn_norm_sd/2), width = 0.0, colour = "darkgrey") +
    geom_errorbarh(aes(xmin=SLN_mean-SLN_sd/2,
                    xmax=SLN_mean+SLN_sd/2), colour = "darkgrey")+
  ylab("Normalised Photosynthetic rate (% maximum)") +
  xlab("Specific Leaf Nitrogen (SLN)") +
  theme(legend.title=element_blank()) +
 # facet_grid(Experiment~.) +
  stat_ellipse(type = "t") +
  theme(legend.title=element_blank()) 

g_norm
```

```{r, fig.height=10, fig.width=8}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}


multiplot(g_abs,g_norm,cols = 1)

```



## Cluster analysis to select cluster number used above

```{r Cluster}


# Used this method: http://rstudio-pubs-static.s3.amazonaws.com/2598_ccd642fc32854463844c6f9cc153983a.html

# This is also good: http://www.statmethods.net/advstats/cluster.html

# select data
mydata <- df_mean

head(mydata)



```

# Plot averages

```{r, include = FALSE}
#plot data
mydata %>%
  na.omit() %>%
  ggplot(aes(x=SLN_mean, y=Pn_mean)) +
  geom_point()
```

```{r, include=FALSE}
# cluster with 1 to 10 cluster
res.kmeans <- lapply(1:10, function(i) { ## this is a list of 10 itens
    kmeans(mydata[,c("SLN_mean","Pn_mean")], centers = i) # function that does kmeans
})

## SS for each cluster (1 cluster to 10 clusters)
lapply(res.kmeans, function(x) x$withinss)

## Sum up SS
res.within.ss <- sapply(res.kmeans, function(x) sum(x$withinss))
```

# Plot cluster number and within cluster sums of squares

```{r, fig.height=8, fig.width=8}
#plot
ggplot(data.frame(cluster = 1:10, within.ss = res.within.ss), aes(cluster, within.ss)) +
  geom_point() + 
  geom_line() +
    scale_x_continuous(breaks = 0:10)
```

## Check all clusters in graph

```{r, include=FALSE, echo=FALSE}
# colour cluster
cluster.colors <- lapply(res.kmeans, function(x) x$cluster)

# loop on graphs
lapply(cluster.colors,
      function(colors) {
          plot.dat <- cbind(mydata, cluster = factor(colors))

          gg.obj <- ggplot(plot.dat, aes(SLN_mean, Pn_mean, color = cluster)) +
              geom_point() + labs(title = paste(nlevels(factor(colors))))

          print(gg.obj)
      })

```

## Plot graph for all raw data with selected cluster number

```{r, fig.height=8, fig.width=8}

colour.selected <- cluster.colors[[3]] # select cluster number here!

col.func <- function(colors) {
          plot.dat <- cbind(mydata, cluster = factor(colors))

          gg.obj <- ggplot(plot.dat, aes(SLN_mean, Pn_mean, color = cluster)) +
              geom_point() + labs(title = paste(nlevels(factor(colors))))

          print(gg.obj) 
}

col.func(colour.selected)


```

